% !TeX root = main.tex

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\subsection{Handbook goals}

This handbook is designed to help students and faculty understand the policies and procedures associated with the Master’s and Ph.D. programs in Computer Science. It is meant to complement, not replace, the Graduate Degree Requirements of the \textit{School of Engineering and Applied Science (SEAS)} and the University of Virginia \textit{(UVA) Graduate Record}.

\subsection{Graduate degrees}

The Department of Computer Science offers three graduate degrees in the
School of Engineering and Applied Science (SEAS).

\begin{itemize}
\item
  \emph{Doctor of Philosophy (PhD).} The Ph.D. program is designed for students interested in academic positions in colleges/universities
  and/or research positions in industrial or commercial laboratories.

\item
  \emph{Master of Science (MS)}. The M.S. degree introduces students to research at the graduate level with a focus on proposing and executing,
  and then documenting a research experience with a formal, written
thesis, and oral presentation.
  
\item
  \emph{Master of Computer Science (MCS)}. The M.C.S. degree is a graduate professional degree with an emphasis on coursework. It enhances the knowledge obtained in an undergraduate program by providing students with broader knowledge and a deeper technical understanding of Computer Science concepts.
\end{itemize}

\subsection{Contacts}


\begin{tabularx}{\textwidth}{|X|l|l|}
    \hline
        \textbf{Position} & \textbf{Name} & \textbf{Contact} \\ \hline
        Master's Graduate Program Director (MGPD) & Prof. Felix Lin & \makecell{\href{mailto:xl6yq@virginia.edu}{{xl6yq@virginia.edu}}} \\ \hline
        PhD Graduate Program Director (PGPD)      & Prof. Felix Lin & \makecell{\href{mailto:xl6yq@virginia.edu}{{xl6yq@virginia.edu}}} \\ \hline
        Ombudsperson & \makecell{Prof. David Evans \\ Prof. Nada Basit} & \makecell{\href{mailto:evans@virginia.edu}{{evans@virginia.edu}}, Rice 507 \\ \href{mailto:basit@virginia.edu}{{basit@virginia.edu}}, Rice 405} \\ \hline
        Graduate Coordinators & \makecell{Jai Maupin \\ Marion Hight}   & \makecell{\href{mailto:jm3xe@virginia.edu}{{jm3xe@virginia.edu}} \\ \href{mailto:qnx5re@virginia.edu}{{qnx5re@virginia.edu}}}  \\ \hline
        CS Department Chair & Prof. Sandhya Dwarkadas & \makecell{\href{mailto:bay7xc@virginia.edu}{{bay7xc@virginia.edu}}, Rice 521} \\ \hline
        CS Director of Operations & Debbie Rose & \makecell{\href{mailto:dcr4f@virginia.edu}{{dcr4f@virginia.edu}}, Rice 526} \\ \hline
        Chair of Graduate Admissions Committee & Prof. Matt Dwyer & \makecell{\href{mailto:md3cn@virginia.edu}{{md3cn@virginia.edu}}, Rice 424} \\ \hline
        SEAS Director of Graduate Programs & Dr. Amy Clobes & \makecell{\href{mailto:amc5hu@virginia.edu}{{amc5hu@virginia.edu}}, \\ Thornton A109} \\ \hline
\end{tabularx}





\subsection{Policy Exceptions}

In rare cases, the Master's Graduate Program Director (MGPD) or the Ph.D. Graduate Program Director (PGPD) may waive a policy or requirement for valid reasons. The term "Graduate Program Director" (GPD) in this handbook refers to either the MGPD or PGPD.