% !TeX root = main.tex


\hypertarget{ph.d.-student-assessment-policy-and-process}{%
\subsection{Ph.D. Student Assessment Policy and Process}\label{ph.d.-student-assessment-policy-and-process}}

\subsubsection{Goal}

The Department of Computer Science is committed to maintaining a strong
and nurturing Ph.D. degree program. To achieve this, the UVA CS Department evaluates the progress of each Ph.D. student. The purpose of this assessment is to provide both the student and their advisor with feedback that will help ensure the student's timely completion of the Ph.D. and support the achievement of their professional goals.

\subsubsection{Process Overview}

Ph.D. students will have their progress and achievements assessed twice a year by their faculty advisor and a three-member faculty committee. The results of the committee's assessment will be shared with both the student and the faculty advisor.

\subsubsection{Ph.D. Student Assessment}

A Ph.D. student assessment committee consists of three faculty members. Students will be randomly assigned to committees, ensuring they are not paired with their advisor or co-advisor. The review load will be evenly distributed among the committees.

Student progress will be evaluated twice a year, at the end of the Spring and Fall terms. 

During each assessment period, the student will fill out a self-assessment form, while their advisor will complete a corresponding assessment form for the student. The student’s assessment committee will review both the student's self-assessment and the advisor's assessment before completing the committee’s assessment form.

The committee and student reports will be submitted to the faculty advisor for feedback. Based on any comments from the faculty advisor, the committee may choose to revise their assessment report. Once the assessment report is finalized, the advisor will meet with the student to review the committee's assessment and discuss plans to address any concerns raised in the report, as well as plans for the next assessment period. 

Please note: To avoid any potential mixed messages and confusion, only the committee's assessment will be provided to the student. However, the advisor may choose to share their own assessment report with the student.

\subsubsection{Assessments of Concern}

In the case of assessments that require further attention, 
the Ph.D. Graduate Program Director (PGPD) will work with the student and their advisor to determine the
appropriate course of action. The PGPD will
also notify the Department Chair of any assessments of concern and
recommended actions.

\subsubsection{Confidential Information}

If a student desires to provide information that is not to be
shared with the advisor, 
the student can provide such information via this feedback form: 

\url{https://app.smartsheet.com/b/form/b5cd18894d8d4479a9696ca07530faa3}

This information will be made available only to the student's assessment committee, the PGPD, the CS Graduate Coordinators, and the Department Chair.
They must not disclose this information to the student's advisor or use it in the student's committee assessment, which will eventually be visible to the advisor.

If the student is an advisee of the Department Chair or the PGPD, any confidential information provided by the student will not be shared with them.
